\begin{center}
% {\fontsize{18pt}{20pt}\selectfont \textbf{\underline{ACKNOWLEDGEMENT}}}
    {\fontsize{18pt}{20pt}\bookmanheading{\underline{ACKNOWLEDGEMENT}}}

\end{center}
\addcontentsline{toc}{section}{ACKNOWLEDGEMENT}

I would like to express my sincere gratitude to all those who have contributed to the successful completion of this doctoral research.

First and foremost, I extend my deepest appreciation to my thesis supervisor for his invaluable guidance, continuous encouragement, and insightful feedback throughout this research journey. His expertise in power electronics and control theory has been instrumental in shaping this work, and his patience and support during challenging phases of the research have been truly invaluable.

Special thanks to Dr. S.P. Singh for his motivation, technical insights and applications in renewable energy systems.

I acknowledge the National Institute of Technology, Uttarakhand, for providing the research facilities, computational resources, and academic environment necessary for conducting this work. I am particularly thankful to the Department of Electrical Engineering for providing access to the OPAL-RT real-time simulator platform, which was crucial for the Hardware-in-Loop validation experiments presented in this thesis.

My sincere thanks to the faculty members and research scholars of NIT Uttarakhand who provided valuable suggestions during research seminars and discussions. Special thanks to  Dr. Prakash Dwivedi for his constructive feedback helped refine the research direction and strengthen the experimental validation framework.

I am deeply indebted to my family for their unwavering love, support, and encouragement throughout my doctoral studies. Their understanding and patience during the long hours of research and writing made this achievement possible.

Finally, I thank all my friends and colleagues who provided moral support and created a positive environment conducive to research and learning.

\vspace{1cm}

\begin{flushright}
\textbf{Ruchir Pandey}\\
National Institute of Technology, Uttarakhand\\
\end{flushright}